DNSKEY Management

### 2012-12-10 paper/paper.tex
Fixes for uppercases after colons

SecSpider \cite{secspider, Osterweil09} is another inline TAR, but
uses a different approach for key validation: Rather then entering and
signing public keys manually, it randomly queries DNSKEY entries from
different point in the world simultaneously and only enters it into
the TAR, if all the received keys match. This makes spoofing of a key
very difficult due to the spatial distribution and the
unpredictability of the queries.

Another type of TAR resides at the resolver: A statically configured
TAR stores keys locally at the resolver and hence does not require to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or may be just a bunch of manually configured trusted keys. As an
example of a statically configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, an addition
%% TODO what does this "plugin" do exactly?
to a standard resolver, \cite{Osterweil09} which can poll keys from
different locations such as web pages, but also also other
vantage-enabled resolvers. Of course, the operator may also choose to
add trusted keys manually.

>>>>

SecSpider \cite{secspider, Osterweil09} is another inline TAR, but
uses a different approach for key validation: rather then entering and
signing public keys manually, it randomly queries DNSKEY entries from
different point in the world simultaneously and only enters it into
the TAR, if all the received keys match. This makes spoofing of a key
very difficult due to the spatial distribution and the
unpredictability of the queries.

Another type of TAR resides at the resolver: a statically configured
TAR stores keys locally at the resolver and hence does not require to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or may be just a bunch of manually configured trusted keys. As an
example of a statically configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, an addition
%% TODO what does this "plugin" do exactly?
to a standard resolver, \cite{Osterweil09} which can poll keys from
different locations such as web pages, but also also other
vantage-enabled resolvers. Of course, the operator may also choose to
add trusted keys manually.
